%-------------------------
% Katy Felkner's 1 page Résumé
% adapted from template by Sourabh Bajaj
% https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\setlength{\footskip}{4.08003pt}

% formatting for links
\usepackage[pdftex]{hyperref}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\hypersetup{colorlinks,breaklinks,linkcolor=darkblue,urlcolor=darkblue,anchorcolor=darkblue,citecolor=darkblue}

% manage publication list
\usepackage[style=authoryear, sorting=ydnt, minnames=2, dashed=false ]{biblatex}
\AtBeginBibliography{\small}

\renewcommand*{\mkbibcompletename}[1]{%
  \ifitemannotation{highlight}
    {\textbf{#1}}
    {#1}  
}

% text encoding stuff to make this ATS-parseable
\input{glyphtounicode}
\pdfgentounicode=1

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black} \titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItemWithHeader}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItem}[1]{
  \item\small{
  {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt} \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \small #4 \\
      
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingSecondTitle}[2]{
  \vspace{-3pt} \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \small #2 \\
    \end{tabular*}\vspace{-5pt}
}

% tentatively keeping this in a tabular to make it more identical to other headings
\newcommand{\resumeSubheadingNoTitle}[1]{
  \vspace{-1pt} \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[label={}, leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\textbf{\LARGE Katy Felkner}

\href{mailto:felkner@isi.edu}{\texttt{felkner@isi.edu}}~\textbar~ \href{http://katyfelkner.com/}{\texttt{http://www.katyfelkner.com}}~\textbar~(405) 808-2703


\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Southern California}{Los Angeles, CA}
      {Ph.D. in Computer Science}{Aug. 2020 -- Present}
      \resumeItemListStart
        \resumeItem{Expected May 2027; GPA: 3.90/4.00; Supported by \textbf{NSF Graduate Research Fellowship}}
      \resumeItem{Selected Coursework: Adv. NLP, Fairness in AI, Probability for Data Sci., Representation Learning in NLP}
      \resumeItemListEnd
      
    \resumeSubheading
      {University of Oklahoma}{Norman, OK}
      {B.S. Computer Science \textit{(summa cum laude)}, B.A. Letters \textit{(summa cum laude)}; GPA: 4.0/4.0}{Aug. 2016 -- May 2020}
  \resumeSubHeadingListEnd

\section{Research Interests}
\small{Research agenda focuses on developing high-quality, \textbf{well-grounded benchmark datasets} for robust evaluation of language models, with particular emphases on community-engaged methods and on rigorous measurement of social bias.}

\section{Technical Skills}
 \resumeSubHeadingListStart
   \resumeItemWithHeader{Programming Languages and Skills}{Python, C, C++, R, SQL, Bash Scripting, HPC, Slurm}
   \resumeItemWithHeader{ML/NLP/Data Science Tools}{HuggingFace, PyTorch, TensorFlow, SpaCy, Pandas, Numpy, Scikit-Learn, NLTK}
 \resumeSubHeadingListEnd


\section{Research Experience}
\resumeSubHeadingListStart
    \resumeSubheading
      {LLM Fairness and Bias, USC Information Sciences Institute}{Los Angeles, CA}
      {Graduate Research Assistant}{Jan. 2022 -- Present}
      \resumeItemListStart
      \resumeItem{Develop two community-sourced benchmark datasets for detecting anti-LGBTQ+ and antisemitic bias in LLMs.}
      \resumeItem{Design and distribute two community surveys and analyze 500 responses to inform LLM bias benchmarks.}
      \resumeItem{Lead team of 3 to collect 8M sentences of community data, then train 32 debiased models via continued pretraining.}
      \resumeItem{Assess LLM capability for  fairness benchmark construction and conduct detailed human analysis of model failures.}
      \resumeItemWithHeader{Mentoring}{Mentor undergrad on project analyzing behavior of textual entailment (NLI) as an LLM bias metric.}
      \resumeItemWithHeader{Publications}{Lead interdisciplinary teams to publish four papers (two ACL, one workshop, one under review).}
      \resumeItemListEnd

    \resumeSubheading
      {Border Translation Project, USC Information Sciences Institute}{Los Angeles, CA}
      {Graduate Research Assistant}{Aug. 2020 -- Dec. 2021}
      \resumeItemListStart
      \resumeItem{Built and evaluated NMT systems for extremely low-resource languages.}
      \resumeItem{Developed NMT system for K'iche', with intended application of providing legal assistance to asylum seekers.}
      \resumeItemListEnd

    \resumeSubheading
      {Ultrascale Systems Research Center, Los Alamos National Laboratory}{Remote}
      {Post-Baccalaureate Research Intern}{May 2020 -- Aug. 2020}
      \resumeItemListStart
      \resumeItem{Tested 16 combinations of word embedding and clustering algorithms to predict failures from supercomputer syslog.} 
      \resumeItemWithHeader{Publication}{Paper accepted to Second Workshop on ML for Computing Systems, Supercomputing 2020.}
      \resumeItemListEnd
      
    \resumeSubHeadingListEnd
\section{Selected Publications}
\begin{refsection}[my_selected_pubs_formatted.bib]
\nocite{*}
\printbibliography[heading=none]
\end{refsection}

\section{Teaching Experience}
\resumeSubHeadingListStart
    \resumeItemWithHeader{USC CSCI 662: Advanced NLP}{\textit{Teaching Assistant} \hfill Aug. 2025 -- Dec. 2025}
    \resumeItemWithHeader{USC CSCI 350: Intro to Operating Systems}{\textit{Teaching Assistant} \hfill May 2025 -- Aug. 2025}
\resumeSubHeadingListEnd


\section{Professional Service}
  \resumeSubHeadingListStart
  \resumeItemWithHeader{Seminar Organizing}{USC ISI Natural Language Seminar \hfill Aug. 2024 -- May 2025}
  \resumeItemWithHeader{Reviewing}{EMNLP 2025 Ethics Review, NAACL SRW 2025, EMNLP 2023, ACL 2023, EMNLP 2022 Theme Track}
    \resumeSubHeadingListEnd

\end{document}
